Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-02 hscc2017/paper.tex
explicitly stated the benchmark
updated median time for 2-stage verification engine

\item Experimental results show that \tool is able to efficiently synthesize
  stable controllers for a set of intricate benchmarks taken from the
  literature: the median runtime for our benchmark set is $197$\,s, i.e.,
  half of the controllers can be synthesized in less than five minutes.

@@

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increases of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is
significantly slower on average and is only useful for benchmarks where
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines independently, where in $16$ out of $23$
benchmarks the two-stage engine is faster.

@@

The median run-time for our benchmark set is $48$\,s, implying that \tool
can synthesize half of the controllers in less than one minute.  Overall,
the average synthesis time amounts to approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}

>>>>

\item Experimental results show that \tool is able to efficiently synthesize
  stable controllers for a set of intricate benchmarks taken from the
  literature: the median runtime for our benchmark set with the two-stage 
  verification engine is $52$\,s, i.e.,
  half of the controllers can be synthesized in less than five minutes.

@@

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increases of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty (represented by $G_{3b}$
in Table~\ref{tab:results}) required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is
significantly slower on average and is only useful for benchmarks where
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines independently, where in $16$ out of $23$
benchmarks the two-stage engine is faster.

@@

The median run-time for our benchmark set with the two-stage verification engine is 
$52$\,s, implying that \tool
can synthesize half of the controllers in less than one minute. Overall,
the average synthesis time amounts to approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}}\footnote{CBMC version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
